---
title: 'Supplement for Johanna Nichols, "Canonical complexity"'
output:
  html_document:
    theme: spacelab
    highlight: pygments
    code_folding: hide
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, fig.width=7.5)
```

### Map

This site is a supplement to Johanna Nichols, Canonical complexity. Peter Arkadiev and Francesco Gardani, eds., Morphological complexity.  Oxford University Press, in press. 

```{r}
library(lingtypology)
library(leaflet.extras)
library(readr)
library(dplyr)
read_csv("opacity.csv") %>% 
  arrange(Opacity) ->
  opacity
map.feature(opacity$language2,
            features = opacity$Opacity,
            label = opacity$Language,
            color = c("white", "lightblue", "black"),
            title = "Opacity") %>% 
  addFullscreenControl()
```

This map created with `lingtyplogy` and `leaflet.extras` packages:

* Moroz G (2018). lingtypology: easy mapping for Linguistic
Typology. URL: <https://CRAN.R-project.org/package=lingtypology>.
* Bhaskar Karambelkar. (2018) leaflet.extras: Extra Functionality
  for 'leaflet' Package.
